---
title: "R notes - basic"
author: "Dongyang Li"
date: "February 29, 2016"
output: html_document
---

##Data types

Every object has to intrinsic attributes: mode and length.

Four kinds of basic mode:

- Character

- Numeric (Integer: Specify the L suffix. For example: 1L)

- Complex

- Logical

Funtion *mode* and *length* can be used to check the attributes of an object respectively.

####Character

Input with " ".

```{r, cache=TRUE}
x <- "double \" quotes"
x
cat(x)#concatenate and print
```

##Overview of types of objects

Only data frame and list allow different modes in a same object.

- Vector

- Factor: categorical variable. numeric or character

- Array: table with k dimontions

- Matrix: an array with k=2

- Data frame: table composed of one or several vectors and/or factors all of the same length but possibly of different modes.

- Time series: time series data set containing additional attributes such as frequency and dates.

- List: can contain any type of objects, including lists

##Missing values and infinite

- NA: missing values (not available)

- NaN: undefied mathematical operations (not a number)

- A NaN value is also NA, but the converse is not true.

- Remove missing valuse

```{r, cache=TRUE}
x <- c(1, 2, NA, 4)
missingvalue <- is.na(x)
x[!missingvalue]
```

- Positive infinity: *Inf*; negative infinity: *-Inf*

##Reading data
#### read.table; read.csv: reading tabular data
  
- header: logical indicating if the file has a header line
  
- sep: a string indicating how the columns are separated
  
- colClasses: a character vector indicating the class of each column in the dataset
  
- comment.char: a character string indicating the comment charachter
  
- skip: the number of lines to skip from the beginning
  
- stringsAsFactors: should character variables be coded as factor?

####readLines: reading lines of a text file

####source: reading in R code files (inverse of dump)

####dget: reading in R code files (inverse of dput)

####load: reading in saved workspaces

####unserialize: reading single R objects in binary form

##Save data

*write.table*

*write(x, file = "table.txt")*

##Generate data
```{r, cache=TRUE}
1:10 - 1
1:(10 - 1)
seq(length = 4, from = 1, to = 5)
seq(1, 5, 2)#from 1 to 5, increment is 2
rep(1, 10)#replicate 1 for 10 times
sequence(4:6)
sequence(c(3,6))
#generate levels
gl(3, 5, labels = c("male", "female", "unknown"))#create 3 levels. the number of each level repeats 5 times
#create a data frame
#it will show all the possible combination of the values from each variable
expand.grid(var1 = c(60, 80), var2 = c(1, 2), gender = c("male", "female"))
#create random sequences
rnorm(10, mean = 2, sd = 3)
#open data editor to input data
x <- c(1,2)
data.entry(x)
```

##Operators
####Arithmetic operators
- +, -, *, /, ^ 

- %%: modulo

- %/%: integer division

####Comparision operators
- <, >, <=, >=, ==, !=

####Logical operator
- !x: logical not x

- x & y: logical and

- x && y: id

- x | y: logical or

- x || y: id

- xor(x, y): exclusive or

*Note: & and && indicate logical AND and | and || indicate logical OR. The shorter form performs elementwise comparisons in much the same way as arithmetic operators. The longer form evaluates left to right examining only the first element of each vector. Evaluation proceeds only until the result is determined. The longer form is appropriate for programming control-flow and typically preferred in if clauses.*
