---
title: "R notes - basic"
author: "Dongyang Li"
date: "February 29, 2016"
output: html_document
---

###1) Data types

- Character

- Numeric

- Integer: Specify the L suffix. For example: 1L

- Complex

- Logical

###2) Missing values

- NA: missing values

- NaN: undefied mathematical operations

- A NaN value is also NA, but the converse is not true.

- Remove missing valuse
```{r, cache=TRUE}
x <- c(1, 2, NA, 4)
missingvalue <- is.na(x)
x[!missingvalue]

```

###3) Data frames

- Used to store tabular values

- Can store different classes of objects in each column;
matices must have the every element be the same class

###4) Names

```{r, cache=TRUE}
x <- 1:3
names(x) <- c("first", "second", "third")
x
names(x)
```

###5) Reading data
- read.table; read.csv: reading tabular data
  
  header: logical indicating if the file has a header line
  
  sep: a string indicating how the columns are separated
  
  colClasses: a character vector indicating the class of each column in the dataset
  
  comment.char: a character string indicating the comment charachter
  
  skip: the number of lines to skip from the beginning
  
  stringsAsFactors: should character variables be coded as factor?

- readLines: reading lines of a text file

- source: reading in R code files (inverse of dump)

- dget: reading in R code files (inverse of dput)

- load: reading in saved workspaces

- unserialize: reading single R objects in binary form

###6) Subsetting lists
```{r, cache=TRUE}
x<- list(a = 1:4, b = 0.6)
x[1]
x[[1]]
```

$ can only be used with literal names

