---
title: "Loop Function"
author: "dongyang Li"
date: "February 29, 2016"
output: html_document
---

###*lapply*
- Loop over a list and evaluate a function on each element

- Three arguments: a list x, a function and ...

- If x is not a list, it need to be coerced to a list using *as.list*

```{r, cache=TRUE}
#Calculate the mean of each element in a list
a <- list(x = 1:5, y = 2:6)
lapply(a, mean)
```

###*sapply*
- same as *lapply* but try to simplify the result

1. If the result is a list where every element is length 1, then a vector is returned.

2. If the result is a list where every element is a vector of the same length(>1), a matrix is returned.

3. If it cannot figure things out, a list is returned.

```{r, cache=TRUE}
a <- list(x = 1:5, y = 2:6)
sapply(a, mean)
```

###*apply*
- Apply a function over the margins of an array

```{r, cache=TRUE}
x <- cbind(x1 = 3, x2 = c(4:1, 2:5))
dimnames(x)[[1]] <- letters[1:8]
apply(x, 1, mean)
```

###*tapply*
- Apply a function over subsets of a vector
```{r, cache=TRUE}
x <- c(rnorm(10), runif(10), rnorm(10))
f <- gl(3, 10) #generate factor levels
f
tapply(x, f, mean, simplify = TRUE)
```

###*mapply*
- Multivariate version of *lapply*

- Apply a function in parallel over a set of arguments

- Example: the following two kinds of code are the same

1. 
```{r, cache=TRUE}
list(rep(1, 4), rep(2, 3), rep(3, 2), rep(4, 1))
```

2. 
```{r, cache=TRUE}
mapply(rep, 1:4, 4:1, SIMPLIFY = TRUE)
```

###*split*
- Takes a vector or other objects and splits it into groups determined by a factor or list of factors

